A thermodynamic view of dusty protoplanetary disks: axisymmetric stability

### 2016-08-23 summary.tex
final fig in place

Fig. \ref{result2d_loren} shows an unstable mode found for this setup,
with  
frequency 
\begin{align*}
\sigma = (0.3631\ii - 0.1251)\hgas\OmK. 
\end{align*}
This growth rate corresponds to $8.8$ orbits, comparable to the $12$
orbits reported by \citeauthor{loren15}. We find this mode 
persists when $q=0$, so it is not the VSI.  For the above parameters
we also estimate a much smaller growth
rate for the streaming instability (using
Eq. \ref{streaming_dispersion}) of 
$O(10^{-3}\hgas\OmK)$, We thus also rule out
SI, as did \citeauthor{loren15}.

\begin{figure}
  \includegraphics[width=\linewidth]{figures/result2d_loren.ps}
  \caption{Possible eigenmode of the dusty instability discovered by 
    \cite{loren15} in their numerical simulations. The growth rate and 
    radial spacing of the `toroidal vortices' are similar to that
    reported by \citeauthor{loren15}. The instability is driven by
    dust-gas drag. The color scale shows the
    perturbed  
    dust-to-gas ratio, $\delta\epsilon$; and the arrows show
    $\sqrt{\rho}\left(\dd v_x, \dd v_z\right)$.
    \label{result2d_loren}
  }
\end{figure}

>>>>

Fig. \ref{compare_eigenvals_ts0d02} shows the unstable modes found for
this setup. We find the usual VSI modes, here with $\omega> 3,\, s<
0.2$. However, we also find the mode marked by the blue asterisk with
frequency 
\begin{align*}
\sigma = (0.3631\ii - 0.1251)\hgas\OmK. 
\end{align*}
This growth rate corresponds to $8.8$ orbits, comparable to the $12$
orbits reported by \citeauthor{loren15}. We visualize this mode in
Fig. \ref{result2d_loren}. We find this mode 
persists when $q=0$, so it is not the VSI. 
Using Eq. \ref{streaming_dispersion} with the above parameters,  
we also estimate a much smaller growth 
rate for the streaming instability of 
$O(10^{-3}\hgas\OmK)$, We thus also rule out
SI, as did \citeauthor{loren15}. However, the mode disappears with
$\tstop=0$, so it is associated with finite dust-gas drag.

\begin{figure}
  \includegraphics[width=\linewidth]{figures/compare_eigenvals_ts0d02}
  \caption{Unstable modes in a locally isothermal, dusty disk
    with stopping time  
    $\tstop=0.02\OmK^{-1}$. Modes with $\omega>3$ are due to
    VSI. The mode marked by the blue asterisk, visualized in
    Fig. \ref{result2d_loren}, is associated with finite dust-gas
    drag.   
    \label{compare_eigenvals_ts0d02}
  }
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{figures/result2d_loren.ps}
  \caption{The mode marked by the blue asterisk in
    Fig. \ref{compare_eigenvals_ts0d02}. This is a possible eigenmode
    of the dusty instability discovered by  
    \cite{loren15} in their numerical simulations. The instability growth timescale and 
    radial spacing of the `toroidal vortices' are similar to that 
    reported by \citeauthor{loren15}. This instability is driven by
    dust-gas drag. The color scale shows the 
    perturbed  
    dust-to-gas ratio, $\delta\epsilon$; and the arrows show
    $\sqrt{\rho}\left(\dd v_x, \dd v_z\right)$.
    \label{result2d_loren}
  }
\end{figure}
